\toolnameend: A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-26 doc/paper.tex
Intro paragraph 1. Fixes #111, fixes #112, fixes #113

	\section{Introduction} Spreadsheets surround us, ordering the ever-growing
	flood of data that we produce. They serve key roles in industry, where as much
	as 95\% of U.S. financial firms use them daily \cite{panko2008sarbanes}, and
	academia, where teachers can use them to track research and students' grades,
	not to mention many other lines of work \cite{ko2011state}. It's this
	flexibility that grants them their allure: while a novice can still work
	without much experience, spreadsheets offer hundreds of specialized functions
	to fulfill a wide range of advanced needs, from complex statistics to text
	manipulation \cite{nardi1990spreadsheet}. As such, it should be no surprise
	that tens of millions of workers rely on these programs every day
	\cite{scaffidi2005estimating}.

>>>>

	\section{Introduction} Spreadsheets surround us. They serve key roles in
	industry, where as much as 95\% of U.S. financial firms use them daily
	\cite{panko2008sarbanes}, and academia, where teachers can use them to track
	research and students' grades, not to mention many other applications
	\cite{ko2011state}. It's this flexibility that grants them their allure: while
	a novice can still work without much experience, spreadsheets offer hundreds of
	specialized functions to fulfill a wide range of advanced needs, from complex
	statistics to text manipulation \cite{nardi1990spreadsheet}. As such, it should
	be no surprise that tens of millions of workers rely on these programs every
	day \cite{scaffidi2005estimating}.
